Topic Modeling of News

### 2017-11-09 paper/R/02_combine.Rmd
add facebook_share api

# number of Facebook shares
okt$fb_shares <- str_extract(okt$shares, "(?<='facebook': )[0-9]*")
okt$fb_shares <- ifelse(is.na(okt$fb_shares),0, okt$fb_shares)
okt$fb_shares <- as.integer(okt$fb_shares)

# Text Length
names(okt) <- gsub("body", "text", names(okt))
okt$text_length <- sapply(gregexpr("\\S+", okt$text), length)

@@

# number of Facebook shares
nov$fb_shares <- str_extract(nov$shares, "(?<='facebook': )[0-9]*")
nov$fb_shares <- ifelse(is.na(nov$fb_shares),0, nov$fb_shares)
nov$fb_shares <- as.integer(nov$fb_shares)

# Text Length
names(nov) <- gsub("body", "text", names(nov))
nov$text_length <- sapply(gregexpr("\\S+", nov$text), length)
```

## Reduce Dataframe
```{r}
keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
keys <- paste(c("bundestagswahl","koalition"), collapse = "|")

@@

@@

## Filtering
```{r}  
btw %>%
  group_by(title, site) %>%
  ungroup() %>%
  arrange(desc(fb_shares)) %>%
  distinct(title,site, .keep_all = TRUE) -> btw

btw %>%
  filter(date < as.Date("2017-10-29")) -> btw
```

@@

## Stemming
```{r}
stem_text<- function(text, language = "porter", mc.cores = 1) {
  # stem each word in a block of text
  stem_string <- function(str, language) {
    str <- strsplit(x = str, split = "\\s")
    str <- wordStem(unlist(str), language = language)
    str <- paste(str, collapse = " ")
    return(str)
  }

@@

@@

>>>>

# number of Facebook shares
okt$fb_shares <- str_extract(okt$shares, "(?<='facebook': )[0-9]*")
okt$fb_shares <- ifelse(is.na(okt$fb_shares),0, okt$fb_shares)
okt$fb_shares <- as.integer(okt$fb_shares)
names(okt) <- gsub("body", "text", names(okt))

@@

# number of Facebook shares
nov$fb_shares <- str_extract(nov$shares, "(?<='facebook': )[0-9]*")
nov$fb_shares <- ifelse(is.na(nov$fb_shares),0, nov$fb_shares)
nov$fb_shares <- as.integer(nov$fb_shares)
names(nov) <- gsub("body", "text", names(nov))
```

## Reduce Dataframe
```{r}
keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
keys <- paste(c("bundestagswahl","Koalition"), collapse = "|")

@@

## Count number of terms in a string
```{r}
btw$text_length <- sapply(gregexpr("\\S+", btw$text), length)
```

@@

## Filtering
```{r}  
btw %>%
  group_by(title, site) %>%
  ungroup() %>%
  distinct(title,site, .keep_all = TRUE) -> btw
```

@@

## Stemming (not applied)
```{r }
stem_text<- function(text, language = "porter", mc.cores = 1) {
  # stem each word in a block of text
  stem_string <- function(str, language) {
    str <- strsplit(x = str, split = "\\s")
    str <- wordStem(unlist(str), language = language)
    str <- paste(str, collapse = " ")
    return(str)
  }

@@

```{r}
load(file="../output/btw_combined.Rda")
```

# Extract FB Shares
```{r}
library(SocialMediaMineR)

facebook <- get_facebook(btw$url[1:100])

page <- readLines(paste0(check,btw$url[i]))

check <- "https://graph.facebook.com/?id="
pattern <- 'share_count\\":[0-9]+'

shares <- NULL

for (i in (length(shares)+1):nrow(btw)){
  page <- readLines(paste0(check,btw$url[i]))
  string <- str_extract(page, pattern)
  shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
  Sys.sleep(10)
}
```

@@

```{r}
url_slice <- split(btw$url, ceiling(seq_along(btw$url)/1000))
file = "../output/urls"

for (i in 1:length(url_slice)){
  url = url_slice[[i]]
  count = as.character(i)
  write.table(url, file=paste0(file,count,".csv"), sep ="\n", 
              row.names = FALSE, quote = FALSE, col.names = FALSE)
}

write.table(urls1, file="../output/urls1.csv", sep ="\n", row.names = FALSE, quote = FALSE)
write.table(urls2, file="../output/urls2.csv", sep ="\n", row.names = FALSE, quote = FALSE)
```

```{r}
library(Rfacebook)

app_id = 1580533335373831
app_secret = "07ecdc314355649e13447278c57627f6"

shares
```
